### 2022-06-13 doc/src/intro.tex
Add counter overflow interrupt from extension Sscofpmf

The {\RISCV} Privileged Architecture gives every interrupt cause at a
hart a distinct \emph{major identity number}, which is the Exception
Code automatically written to CSR \z{mcause} or \z{scause} on an
interrupt trap.
Interrupt causes that are standardized by the Privileged Architecture
have major identities in the range 0--15, while numbers 16 and higher
are officially available for platform standards or for custom use.
The Advanced Interrupt Architecture claims further authority over the
even identity numbers in the range 16--62, leaving the odd numbers in
that range and all major identities 63 and higher still free for custom
use.
Table~\ref{tab:interruptIdents} characterizes all major interrupt
identities with this extension.

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|l|}
\hline
Major identity & Minor identity & \\
\hline
\hline
0              & --             & \em Reserved by Privileged Architecture \\
\hline
1              & --             & Supervisor software interrupt \\
2              & --             & Virtual supervisor software interrupt \\
3              & --             & Machine software interrupt \\
\hline
4              & --             & \em Reserved by Privileged Architecture \\
\hline
5              & --             & Supervisor timer interrupt \\
6              & --             & Virtual supervisor timer interrupt \\
7              & --             & Machine timer interrupt \\
\hline
8              & --             & \em Reserved by Privileged Architecture \\
\hline
9              & \multicolumn{1}{l|}{Determined by}
                                & Supervisor external interrupt \\
10             & \multicolumn{1}{l|}{\ external interrupt}
                                & Virtual supervisor external interrupt \\
11             & \multicolumn{1}{l|}{\ controller}
                                & Machine external interrupt \\
\hline
12                   & -- & Supervisor guest external interrupt \\
13--15               & -- & \em Reserved by Privileged Architecture \\
\hline
\hline
even numbers, 16--62 & -- & Local interrupts, \emph{or reserved} \\
odd numbers, 17--63  & -- & \em Designated for custom use \\
\hline
$\geq \mbox{64}$     & -- & \em Designated for custom use \\
\hline
\end{tabular}
\end{center}
\caption{%
Major and minor identities for all interrupt causes at a hart.
Major identities 0--15 are the purview of the {\RISCV} Privileged
Architecture.%
}
\label{tab:interruptIdents}
\end{table*}

>>>>

The {\RISCV} Privileged Architecture gives every interrupt cause at a
hart a distinct \emph{major identity number}, which is the Exception
Code automatically written to CSR \z{mcause} or \z{scause} on an
interrupt trap.
Interrupt causes that are standardized by the Privileged Architecture
have major identities in the range 0--15, while numbers 16 and higher
are officially available for platform standards or for custom use.
The Advanced Interrupt Architecture claims further authority over
identity numbers in the ranges 16--23 and 32--47, leaving numbers in the
range 24--31 and all major identities 48 and higher still free for custom
use.
Table~\ref{tab:interruptIdents} characterizes all major interrupt
identities with this extension.

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|l|}
\hline
Major identity & Minor identity & \\
\hline
\hline
0              & --             & \em Reserved by Privileged Architecture \\
\hline
1              & --             & Supervisor software interrupt \\
2              & --             & Virtual supervisor software interrupt \\
3              & --             & Machine software interrupt \\
\hline
4              & --             & \em Reserved by Privileged Architecture \\
\hline
5              & --             & Supervisor timer interrupt \\
6              & --             & Virtual supervisor timer interrupt \\
7              & --             & Machine timer interrupt \\
\hline
8              & --             & \em Reserved by Privileged Architecture \\
\hline
9              & \multicolumn{1}{l|}{Determined by}
                                & Supervisor external interrupt \\
10             & \multicolumn{1}{l|}{\ external interrupt}
                                & Virtual supervisor external interrupt \\
11             & \multicolumn{1}{l|}{\ controller}
                                & Machine external interrupt \\
\hline
12                   & -- & Supervisor guest external interrupt \\
13                   & -- & Counter overflow interrupt \\
14--15               & -- & \em Reserved by Privileged Architecture \\
\hline
\hline
16--23         & --       & \em Reserved for standard local interrupts \\
24--31         & --       & \em Designated for custom use \\
32--47         & --       & \em Reserved for standard local interrupts \\
$\geq \mbox{48}$ & --     & \em Designated for custom use \\
\hline
\end{tabular}
\end{center}
\caption{%
Major and minor identities for all interrupt causes at a hart.
Major identities 0--15 are the purview of the {\RISCV} Privileged
Architecture.%
}
\label{tab:interruptIdents}
\end{table*}
